\documentclass[letter, 14pt]{article}
\usepackage{TLCresume}
\begin{document}


\subsection{Research Engineer \hfill \textit{\textmd{02/25 - Present/}}}
\subtext{\href{https://www.linkedin.com/company/huawei}{\color{black}{Huawei}} \hfill}
\begin{zitemize}
\item Conference Paper: Measuring phonetic distance between cross-lingual character pairs, at IEEE SIU 2025 Conference. \href{https://ieeexplore.ieee.org/abstract/document/11112305}{\color{black}\externallink} \\
\item 1\% improvement to accuracy in ranking pipeline via the addition of phonetic feature, 2\% improvement to translation accuracy on Cyrillic and Arabic queries.
\item AB Test Planning, Creation and Tracking: Tracked 120+ AB tests on 7 major regions over 8 sprints.
\item Extract query-app embeddings, build \& train two-tower type models to improve recall and recommendation quality.
\item Develop velocity-based features with periodical query-app data to improve the ranking model, helping the cold start problem.
\item Also worked on Query Augmentation, Query Correction, Query Prefix and Shortname match algorithms to improve recall. Overall DTR and Revenue change 1.7\% and 8.6\% respectively. 
\end{zitemize}

%====================
% EXPERIENCE A
%====================
\subsection{AI Researcher \& Engineer \hfill \textit{\textmd{10/23 - 10/24}}}
\subtext{\href{https://www.linkedin.com/company/mogram}{\color{black}{Mogram}} \hfill}
\begin{zitemize}
\item Mass \& Tumour \& Calcification segmentation with various encoder-decoder networks.
\item Used patch-based transformer encoder-decoder network to enhance f1 and box f1 scores by around 10\%.
\item R\&D of the segmentation training pipeline with MLflow.
\item Combined \href{https://www.epfl.ch/labs/ivrl/research/slic-superpixels/}{\color{black}{SLIC}} algorithm with adaptive thresholding to gain roughly 10x speed over CPU-bound processes.
\item Design of on-premise service authentication and encryption routines.
\item Anonymization of the DICOM file structure and organization of datasets.
\item Resolved Docker and MongoDB issues in a remote setup. 
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{AI Team Member \& Participant \& Lecturer \hfill\textit{\textmd{{\tiny$\sim$} 02/21 - Present}}}
\subtext{\href{https://inzva.com/}{\color{black}{Inzva}}}
\begin{zitemize}
\item Design and tracking of learning materials as a member of the AI Team.
\item Gave lectures on Structures of ML projects and Computer Vision Fundamentals.
\item Google Tensorflow Developer \& DL Specialization certificates.
\item Worked with Mamba architecture on State Space Tracking/Modelling of Transformer-based LLMs.
\item Application of various deep learning models and study programs to solve real-life and designed challenges for peer learning.
\end{zitemize}


%====================
% EXPERIENCE C
%====================
\subsection{AI Research Student \hfill \textit{\textmd{ 06/22 - 10/23}}}
\subtext{\href{https://www.asillab.com/}{{\color{black}{ASIL Laboratories}}} \hfill}
\begin{zitemize}
\item Dataset creation, labelling \& preprocessing of medical histopathology images.
\item Segmentation for pixel-wise tumour detection, f1 over 70\% with unified resampling for post-processing.
\item Image augmentation techniques with Autoencoder and Diffusion models
\item Published abstract on 
\href{https://arxiv.org/abs/2504.05219}{\color{black}{arxiv. \externallink}}
\end{zitemize}


%====================
% EXPERIENCE D
%====================
\subsection{Machine Learning Intern \hfill \textit{\textmd{ 07/22 - 08/22}}}
\subtext{\href{https://optiwisdom.com/}{{\color{black}{Optiwisdom}}} \hfill}
\begin{zitemize}
\item Integration of the customer database into NoSql.
\item Various ML methods (boosting \& tree algorithms) for revenue prediction.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%%% \subsection{Intern / Machine Workshop \hfill \textit{\textmd{ 01/2022 - %%% 02/2022 }}}
%%% \subtext{\href{http://www.pro-ser.com/index_en.htm}{{\color{black}{Pro-Ser Laboratory Equipments and Automation}}}}
%%% \begin{zitemize}
%%% \item Manufacturing processes of industrial test devices.
%%% \item Machine part drawings on Solidworks.
%%% \item API for the government wastewater surveillance system.
%%% \end{zitemize}


%====================
% EXPERIENCE F
%==================== 


\end{document}